%!TEX root = ../main.tex
\documentclass[../main]{subfiles}

\begin{document}

\newpage
\phantomsection
\section*{Список использованных источников}
\addcontentsline{toc}{section}{Список использованных источников}

\begin{english}
\begin{biblenum}

    \bibitem{GDPR} General Data Protection Regulation, GDPR homepage. URL: \url{https://gdpr.eu} (дата обращения 14.02.2021).
    
    \bibitem{MDPI5} Zimmeck, S., Story, P., Smullen, D., Ravichander, A., Wang, Z., Reidenberg, J.R., Russell N.C., Sadeh, N.: MAPS: Scaling Pri-vacy Compliance Analysis to a Million Apps. In: Proceedings on Privacy Enhancing Technologies, 66, 2019, \url{https://ir.lawnet.fordham.edu/faculty_scholarship/1040}.

    \bibitem{MDPI6} Oltramari, A., Piraviperumal, D., Schaub, F., Wilson, S., Cherivirala, S., Norton, T., Russell, N., Story, P., Reidenberg, J., Sadeh, N.: PrivOnto: A semantic framework for the analysis of privacy policies. Semantic Web, 9(2), 2018; pp. 185-203.

    \bibitem{MDPI9} Kumar V.B., Iyengar R., Nisal N., Feng Y., Habib H., Story P., Cherivirala S., Hagan M., Cranor L., Wilson C., Schaub F., and Sadeh N.: Finding a Choice in a Haystack: Automatic Extraction of Opt-Out Statements from Privacy Policy Text. In: Pro-ceedings of The Web Conference 2020 (WWW ’20), pp. 1943-1954. New York, NY, USA, Association for Computing Machin-ery, 2020. 

    \bibitem{MDPI7} Palmirani, M., Martoni, M., Rossi, A., Bartolini, C., Robaldo, L.: Legal ontology for modelling GDPR concepts and norms. Legal Knowledge and Information Systems. IOS Press, 2018. doi: \url{https://doi.org/10.3233/978-1-61499-935-5-91}.

    \bibitem{MDPI8} Pandit, H. J., O’Sullivan D., Lewis D. An Ontology Design Pattern for Describing Personal Data in Privacy Policies. WOP@ISWC, 2018.

    \bibitem{MDPI10} Sathyendra, K. M., Schaub, F., Wilson, S., Sadeh., N.: Automatic extraction of opt-out choices from privacy policies. In Proc. AAAI Symposium on Privacy-Enhancing Technologies, AAAI Fall Symposium - Technical Report, 2016.

    \bibitem{MDPI11} Ashley, P., Hada, S., Karjoth, G., Schunter, M.: E-p3p privacy policies and privacy authorization. In: Proc. of the ACM work-shop on Privacy in the Electronic Society (WPES 2002), Washington, DC, USA, 2002. 

    \bibitem{MDPI12} Karjoth, G., Schunter, M.: Privacy policy model for enterprises. In: Proc. of the 15th IEEE Computer Security Foundations Workshop, Cape Breton, Nova Scotia, Canada, 2002. 
    
    \bibitem{MDPI13} Ardagna, C.A., De Capitani di Vimercati, S., Samarati, P.: Enhancing User Privacy Through Data Handling Policies. In: Damiani E., Liu P. (eds) Data and Applications Security XX. DBSec 2006. Lecture Notes in Computer Science, vol. 4127. Springer, Berlin, Heidelberg, 2006. 

    \bibitem{MDPI14} Pardo, R., Le Métayer, D.: Analysis of Privacy Policies to Enhance Informed Consent. In: Foley S. (eds) Data and Applica-tions Security and Privacy XXXIII. DBSec 2019. Lecture Notes in Computer Science, vol. 11559. Springer, Cham, 2019. 

    \bibitem{MDPI15} Gerl, A., Bennani, N., Kosch, H., Brunie, L.: LPL, Towards a GDPR-Compliant Privacy Language: Formal Definition and Us-age. Trans. Large-Scale Data- and Knowledge-Centered Systems 2018, 37, pp. 41-80. 

    \bibitem{MDPI16} NIST Privacy Risk Assessment Methodology (PRAM). Available online: \url{https://www.nist.gov/itl/applied-cybersecurity/privacy-engineering/resources} (accessed on 30 March 2021).

    \bibitem{MDPI17} De, S.J., Le Metayer, D.: Privacy Risk Analysis to Enable Informed Privacy Settings. In: 2018 IEEE European Symposium on Security and Privacy Workshops (EuroS\&PW), London, pp. 95-102, 2018. 

    \bibitem{P2Onto} Evgenia Novikova, Elena Doynikova, and Igor Kotenko. P2Onto: Making Privacy Policies Transparent. Springer, 2020.

    \bibitem{MDPI2} Children's Online Privacy Protection Rule ("COPPA"). Available online: \url{https://www.ftc.gov/enforcement/rules/rulemaking-regulatory-reform-proceedings/childrens-online-privacy-protection-rule} (accessed on 30 March 2021). 

    \bibitem{MDPI3} Health Information Privacy. Available online: \url{https://www.hhs.gov/hipaa/index.html} (accessed on 30 March 2021).

    \bibitem{MDPI18} The Usable Privacy Policy Project. Available online: \url{https://usableprivacy.org/} (accessed on 30 March 2021).

    \bibitem{MDPI4} Novikova, E., Doynikova, E., Kotenko, I.: P2Onto: Making Privacy Policies Transparent. In Proceedings of The 3rd Interna-tional Workshop on Attacks and Defenses for Internet-of-Things (ADIoT 2020), In Conjunction with ESORICS 2020. 4-6 No-vember 2020, Paris, France. Computer Security, Lecture Notes in Computer Science (LNCS), Springer, 2020; vol. 12501; pp. 235-252. DOI: \url{https://doi.org/10.1007/978-3-030-64330-0_15}

    \bibitem{MDPI22} PROV\_O: The PROV Ontology Homapage. Available online: \url{https://www.w3.org/TR/prov-o/#Agent} (accessed on 30 March 2021).

    \bibitem{LSA} Landauer, T. K., Foltz, P. W., and Laham, D. An Introduction to Latent Semantic Analysis. Discourse Processes, 25, 1998, pp. 259-284. DOI: \url{https://doi.org/10.1080/01638539809545028}.

    \bibitem{Gensim} Gensim topic modeling library, Gensim homepage. URL: \url{https://radimrehurek.com/gensim} (дата обращения 14.02.2021).

    \bibitem{Polisis} Hamza Harkous, Kassem Fawaz, Remi Lebret, Florian Schaub3, Kang G. Shin, and Karl Aberer. Polisis: Automated Analysis and Presentation of Privacy Policies Using Deep Learning. 2018. \href{https://arxiv.org/abs/1802.02561v2}{arXiv:1802.02561v2}.

    \bibitem{POS} Sachini Weerawardhana, Subhojeet Mukherjee, Indrajit Ray, and Adele Howe. Automated Extraction of Vulnerability Information for Home Computer Security, pages 356-366. Springer, 2015. DOI: \url{https://doi.org/10.1007/978-3-319-17040-4_24}.

    \bibitem{NLTK} Natural Language ToolKit, Analyzing Sentence Structure, NLTK home\-page. URL: \url{https://www.nltk.org/book/ch08.html} (дата обращения 14.02.2021).

    % \bibitem{MDPI19} IoT Security Compliance Framework. Available online: \url{https://www.iotsecurityfoundation.org/best-practice-guidelines/} (accessed on 30 March 2021). 

    % \bibitem{MDPI20} GSMA IoT Security Guidelines and Assessment. Available online: \url{gsma.com/iot/iot-security/iot-security-guidelines/} (ac-cessed on 30 March 2021). 
    
    % \bibitem{MDPI21} Data privacy vocabularies and controls community group. Available online: \url{https://www.w3.org/community/dpvcg/} (ac-cessed on 30 March 2021).

    % \bibitem{MDPI23} The Usable Privacy Policy Project Data and Tools. Available online: \url{https://usableprivacy.org/data} (accessed on 30 March 2021).

    % \bibitem{MDPI24} California Consumer Privacy Act 2018. Available online: \url{https://oag.ca.gov/privacy/ccpa} (accessed on 30 March 2021). 

    % \bibitem{MDPI25} August Device and Service Privacy Policy Homepage. Available online: \url{https://august.com/pages/privacy-policy#product} (accessed on 30 March 2021).

    % \bibitem{Lockdown} Electronic Passes in Moscow during lockdown. URL: \url{https://www.cnews.ru/news/top/2020-05-25_moskovskij_sajt_s_propuskami} (дата обращения 14.02.2021).

\end{biblenum}
\end{english}

\end{document}